RQ2_main

### 2024-12-09 copy_nakiyah.qmd
adding a copy of nakiyah script for testing

```{r echo = FALSE, results = FALSE}
file_path <- "/Users/nakiyahdhariwala/StatsProject/39096-0001-Data.rda"

@@

```{r echo=FALSE, results=FALSE}
# Calculate the ROC curve
roc_curve <- roc(test_data$ImportanceOfStoppingDiscriminationAgainstMinorities, 
                 predicted_probs_stepwise, 
                 levels = c("Not important", "Important"))

# Print the AUC
auc_value <- auc(roc_curve)
cat("AUC:", auc_value, "\n")

# Plot the ROC curve
plot(roc_curve, col = "blue", main = "ROC Curve")
abline(a = 0, b = 1, col = "red", lty = 2)  # Add diagonal line for random guess

# Save the ROC plot
ggsave("roc_curve_plot.png", width = 8, height = 6)

>>>>

```{r echo = FALSE, results = FALSE}
file_path <- "//Users/pdeguz01/Documents/git/Data/2020 CMPS/DS0001/39096-0001-Data.rda"

@@

```{r echo=FALSE, results=FALSE}
# # Calculate the ROC curve
# roc_curve <- roc(test_data$ImportanceOfStoppingDiscriminationAgainstMinorities, 
#                  predicted_probs_stepwise, 
#                  levels = c("Not important", "Important"))
# 
# # Print the AUC
# auc_value <- auc(roc_curve)
# cat("AUC:", auc_value, "\n")
# 
# # Plot the ROC curve
# plot(roc_curve, col = "blue", main = "ROC Curve")
# abline(a = 0, b = 1, col = "red", lty = 2)  # Add diagonal line for random guess
# 
# # Save the ROC plot
# ggsave("roc_curve_plot.png", width = 8, height = 6)
